%------------------------
% Resume
% Author : Piotr Ostrowski
% Github : https://github.com/piotrostr
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\setlength{\footskip}{3.60004pt}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
   }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Piotr Ostrowski}} & Email: \href{mailto:}{piotr.ostrowski@aol.com}\\
  \href{https://piotrostr.com}{Portfolio: piotrostr.com} & Mobile~~+48602490248 \\
  \href{https://github.com/piotrostr}{Github: ~~github.com/piotrostr} \\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lancaster University}{Lancaster, United Kingdom}
      {BSc with Hons Finance and Economics}{October 2019 - Present}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Quantitative Finance, Econometrics, Mathematical Economics, Financial Markets}}}
    \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Skills Summary} \resumeSubHeadingListStart
  \resumeSubItem{Languages}{~~~~~~Python, TypeScript, Solidity, Golang, CSS, Bash}
  \resumeSubItem{Frameworks}{~~~~PyTorch, Flask, ONNX, TensorFlow, Django, Hardhat, React, NestJS, Amplify}
  \resumeSubItem{Tools}{~~~~~~~~~~~~~~Docker, Terraform, Kubernetes, Git, Nginx, Pytest, Mocha, GraphQL, PostgreSQL, MongoDB}


\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{ExpoitOPS (small Poker software start-up}{Remote}
    {Full Stack Developer}{August 2020 – February 2021}
    \resumeItemListStart
        \resumeItem{Discussion Forum Upgrades}
          {Achieved +90\% accuracy designing algorithms for continuous real-time online poker detection and recognition}
          \resumeItem{Training and inference of computer vision AI model}
          {Created an algorithm to detect and recognize cards YOLOv4 model and OCR networks and achieved over 95\% accuracy.}
          \resumeItem{Acceleration of inference}
          {Exported all of the algorithm's models into TensorRT and obtained nearly 10x speed-up.}
      \resumeItemListEnd

    \vspace{2pt}
    \resumeSubheading{Health Token LTD (\$HELTH)}{Remote}
        {Lead Developer}{August 2020 – June 2021}
    \resumeItemListStart
        \resumeItem{Health Token cryptocurrency}
        {Created a token to reward creators in the health industry for sharing their knowledge.}
        \resumeItem{Mobile Application}
        {Coded a Health Handler iOS app that allows users to use the \$HELTH knowledge base to create personalised meal plans using the 'tinder-swipe' functionality.}
        \resumeItem{Impact}
        {The Health's community reached over 2000 users and the token reached a peak market cap of \$1.6m}
        \resumeItemListEnd

    % SMPLverse - AI/Blockchain Developer 28/02/2022 - 24/06/2022 Development and
    % deployment of a crypto web application that uses face detection and recognition
    % networks to match a user's webcam image against a synthetically generated art.
    % Creation, setup and maintenance of the server architecture to handle the launch
    % load. Development of the collection’s NFT smart-contract on ethereum mainnet,
    % maitenance of the metadata server and IPFS content delivery.
    \vspace{2pt}
    \resumeSubheading{Health Token LTD – CTO \& Lead Developer August 2020 – June 2021}{Remote}
        {Instructor (Part-time, Contractual)}{Dec 2018 -  Present}
    \resumeItemListStart
        \resumeItem{Project Course - Find Movie Similarity from Plot Summaries}
        {Created project based course using Unsupervised learning and natural language processing.}
        \resumeItem{Tutorial - Introduction to Reinforcement Learning}
        {Created tutorial for Q-learning RL algorithm and  concepts.}
        \resumeItem{Impact}
        {Course has been taken by 250+ students so far with 4.65 average rating.}
        \resumeItemListEnd

        % TIPMI LIMITED - AWS/React Native Developer
        % 08/12/2021 - 02/02/2022
        % Polishing an iOS mobile application for a Stella Artois partner
        % company, aiming to gather members of the hospitality industry and
        % facilitate the process of tipping. Implementing new features and
        % debugging existing ones in Agile sprint-based workflow.
\resumeSubHeadingListEnd


% Projects
%  MDAPy (University of Calgary) – React and Python Developer June 2021 – July 2021
% Created and deployed a geology web-app (temp website: https://mdapyfrontendmaster.gatsbyjs.io/) that collects
% data to be fed into the backend where geologic methods are applied to produce summary tables and various graphs.

% EduLAB / pTAG – Computer Vision Engineer July 2021 – Present
% Research and evaluation of cutting-edge eye-tracking papers and ways of intrinsic and extrinsic camera calibration.
% Implementation of papers, development of non-hardware AI based eye-tracking solution to be used to collect data
% with an ultimate goal of training another model for detecting Autism spectrum disorders among children.
% Development of APIs and client-side bindings (Nextjs) for utilizing the solution, deployment onto AWS and scaling

% Guardian Protocol - Blockchain Developer
% 27/09/2021 - 2/11/2021
% Development of a full stack DeFi yield web application. Research and
% development of smart-contracts implementing zero-coupon DAI bonds and
% a creation of a frontend interface for calling the contracts’
% methods.

\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Vison - multimedia search engine (NLP, Search Engine, Web Crawlers, Multimedia Processing)}{(Work in progress) Research oriented, open source, search engine for bringing reverse multimedia search to small \& mid scale enterprises. Tech: Python, NodeJS, Intel OpenVino Toolkit, Selenium, TensorFlow (October '18)}
\vspace{2pt}
\resumeSubItem{Reinforcement Learning based Traffic Control System (Reinforcement Learning, Computer Vision)}{AI model to resolve city traffic around 50\%
faster. Tech: Python, Alibaba Cloud, Raspberry Pi, Arduino, SUMO \& OpenCV. (August '18)}
\vspace{2pt}
\resumeSubItem{Panorama from Satellite Imagery using Distributed Computing (Distributed Computing, Image Processing)}{Images clicked using drones, provided by ISRO were stitched together using distributed public compute nodes, effectively bringing down processing time exponentially. Tech: PHP, C++, Java, Python (March '18)}
\vspace{2pt}
\resumeSubItem{Drag-n-drop machine learning learning environment (Web Development, Machine Learning)}{Scratch like tool for implementing machine learning pipelines along with built in tutorial for each concept. Tech: Python, JavaScript (September '18)}
\vspace{2pt}
\resumeSubItem{Search Engine and Social Network(Web Development, Web Crawler, Search)}{Created from scratch a social network and a search engine based on the idea of integrating Facebook and Google. The launched website was among top 1000 websites in India during 2012-2013. Tech: PHP, MySQL, HTML, CSS, WebSockets, JavaScript, RSS, XML ( May '12)}
\resumeSubHeadingListEnd
\vspace{-5pt}

\vspace{-5pt}
\section{Volunteer Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Lancaster University Investment and Finance Society – VP IT}{Lancaster, United Kingdom}
    {Developed and maintained the society's website for 500+ members}{June 2020 – January 2021}
\vspace{5pt}
    \resumeSubheading
    {Lancaster University Ghosal Investment Fund – Portfolio Manager}{Lancaster, United Kingdom}
    {Automated the retrieval of financial data to display portfolio metrics for 58 analysts}{January 2020 – June 2020}

\resumeSubHeadingListEnd

\end{document}
